### 2022-01-17 src-latex/parts/50-xp-setup.tex
One sentence per line
Add protocol figs

% !TeX root = ../main-paper.tex
\section{Experimental Setup}

\subsection{Metrics}
\bertrand{Move after section Cases studies? }
\begin{itemize}
    \item NER quality: Precision, Recall, F1 score (idea: stick with standard spacy/sklearn metrics) \nathalie{Dans la plupart des articles que j'ai lus, c'est toujours une F-mesure qui est utilisée et parfois la précision et le rappel sont ajoutés.}
    \item OCR accuracy: outputs from standard tools (beware of unknown glyphs: do we need any special care?) \nathalie{Pour l'instant, j'ai croisé: CER, WER, Levenshtein et Jaccard. J'ai encore un état de l'art à lire sur le sujet: il y aura probablement d'autres mesures mentionnées.}

@@

\subsection{Cases studies}
\subsubsection{Experiment 1: NER sensibility to the number of training samples}
The first experiment evaluates the performances of the three models on training sets of different sizes. To do so we split the gold reference into a training set, a development set and a test set. The training set is then gradually reduced in size while maintaining the relative frequency of directories within. The training and testing procedure is the same for the three models.

As the form an structure of entries varies across directories collections and through time, the models may learn to overfit on a subset of directories with specific features. To reduce the evaluation bias we start by leaving out 3 directories (1690 entries, ~20\%) from the gold reference to test each model on unseen directories. Then a stratified sampling based on the entry directory name is applied to the remaining set to create a training (6373 entries, ~71\% of the gold reference) and a development set (709 entries, ~8\%). This sampling procedure is a convenient way to shape both sets to reflect the diversity of directories within the gold reference.

>>>>

% !TeX root = ../main-paper.tex
\section{Experiment 1: NER sensibility to the number of training samples}

\begin{figure}[tb]
\includegraphics[width=\linewidth]{figs/protocol.pdf}
\caption{Scheme of the evaluation protocol.}
\label{fig.protocol}
\end{figure}

\subsection{Evaluation protocol \& Metrics}

\Cref{fig.protocol} depicts the evaluation procotol used to assess the OCR and NER systems. Two quality evaluation
are performed in the pipeline named respectively \emph{OCR Q.A.} and \emph{NER Q.A.}.

First the layout extraction and the entry segmentation of the page are performed with a semi-automated system and
checked by a human. Afterward, an OCR system runs on the thumbnails of each segmented entry to extract its text. An
entry might span over multiple text lines but is always single-block. Thus, the most adapted mode is chosen when
the OCR system allows for detection mode (e.g. the \emph{block} mode for \emph{Tesseract}).

\textbf{OCR Q.A.} is performed after some text normalization of the OCR system outputs. Text normalization consists in
projecting unicode characters onto the latin-1 charset (whenever it makes sense) and removing extra symbols (hands,
crosses). Then, the predicted text is aligned with the reference text using standard tools and the Character Error Rates
(CER) are computed at entry level and at global level.

\begin{align}
\mathrm{CER} &=  \frac{\#Errors}{\text{Reference Text Length}} & & \mathrm{CER}_\mathrm{norm} =  \frac{\#Errors}{\text{Alignment Length}} 
\end{align}

In this benchmark, we consider 3 OCR systems well-known for the historical document analysis: Pero OCR, Tesseract and Kraken.

\edwin{FIXME: add ref papier eval OCR + ISRI, eval KRAKEN}

Next, a NER system extracts the named entities from the text of each entry outputed by the OCR and the \textbf{NER Q.A.}
is performed. The NER system outputs a text with tags that enclose the entities. To assess the quality of the entity
extraction, we rely on the same technique as for the OCR evaluation. The predicted text is aligned with the reference
text and the tags are projected in the alignment. Then, the CER is computed between each entity of the alignment and the
groundtruth as illustrated on \cref{fig.eval-ocr-ner}.

\bertrand{Move after section Cases studies? }
\begin{itemize}
    \item NER quality: Precision, Recall, F1 score (idea: stick with standard spacy/sklearn metrics) \nathalie{Dans la plupart des articles que j'ai lus, c'est toujours une F-mesure qui est utilisée et parfois la précision et le rappel sont ajoutés.}
    \item OCR accuracy: outputs from standard tools (beware of unknown glyphs: do we need any special care?) \nathalie{Pour l'instant, j'ai croisé: CER, WER, Levenshtein et Jaccard. J'ai encore un état de l'art à lire sur le sujet: il y aura probablement d'autres mesures mentionnées.}

@@

\subsection{Cases studies}
\subsubsection{Experiment 1: NER sensibility to the number of training samples}
The first experiment evaluates the performances of the three models on training sets of different sizes.
To do so, we split the gold reference into a training set, a development set, and a test set. The training set is then gradually reduced in size while maintaining the relative frequency of directories within.
The training and testing procedure is the same for the three models.

As the form and structure of entries varies across directory collections and through time, the model may learn to overfit on a subset of directories with specific features.
To reduce the evaluation bias, we start by leaving out 3 directories (1690 entries, ~20\%) from the gold reference to test each model on unseen directories.
Then a stratified sampling based on the entry directory name is applied to the remaining set to create a training (6373 entries, ~71\% of the gold reference) and a development set (709 entries, ~8\%).
This sampling procedure is a convenient way to shape both sets to reflect the diversity of directories within the gold reference.
